
---
title: "Introduction to RPGcharacter"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to RPGcharacter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Welcome to RPGcharacter!

The **RPGcharacter** package helps you create and manage RPG game characters
with simple commands.

## Creating a Character

Use the `create_character()` function to interactively create a character:

```{r, eval=FALSE}
library(RPGcharacter)
hero <- create_character()
```

## Summary for a Character

Use the `summary()` function to get a summary of the character's stats:
```{r, eval=FALSE}
library(RPGcharacter)
summary(hero)
```

## Plot the Experience bar for the Character

use the `plot()` function to get a plot of the XP bar 
```{r, eval=FALSE}
library(RPGcharacter)
plot(hero)
```

## Print information about the Character

use the `print()` function to get information about the character
```{r, eval=FALSE}
library(RPGcharacter)
print(hero)
```

## Give the Character intial stats 

use the `Determine_stats(race,class)` function to give the character initial 
stats.
The function is automatically used in `create_character()` function
```{r, eval=FALSE}
library(RPGcharacter)
Determine_stats("Orc", "Mage")
```

## Update the stats of the Character as it levels up

use the `Update_stats()` function to interactively update stats
```{r, eval=FALSE}
library(RPGcharacter)
hero <- Update_stats(hero)
```



## Update the Character's XP and level

use the `level_XP_update()` function, to interactively give the character XP
```{r, eval=FALSE}
library(RPGcharacter)
hero <- level_XP_update(hero,250)
```




